Browsing the Web of Factual Claims

### 2008-09-16 papers/web_of_ideas/web_of_ideas.tex
More minor tidy ups - removing the frame from the popup point browser
More fleshed out. Starting to write about the user studies

@@

@@

@@

@@

@@

@@

Google Notebook
Trailfire
Zotero~\cite{zotero} is a citation mangament tool. Find and organise sources, while recording author, date etc by understanding pages. Can add notes to sources.

@@

\subsection{Recruitment}
Our user study participants were selected from a pool of respondents to a Craigslist posting for people who use the internet as one of their primary sources of information, regularly gather and share this information, and are interested in a new application to facilitate that process. We chose participants based on their responses to the following questions:
\begin{enumerate}
	\item What topics or types of information do you usually look for on the internet?
	\item How do usually go about finding information? (e.g. google, digg, friends, etc)
	\item How do you organize the information you find? (e.g. text file, paper, wiki, etc)
	\item How do you share information with others? (e.g. blog posts, comments, email, facebook, etc)
\end{enumerate}
We preferred individuals who search the internet for research and reading news rather than online shopping, as well as those interested in social and collaborative web activities like social networking web sites.  We were also interested in those who seemed to express a need for our application: people who copy-and-paste text from web pages into word processing documents, or who regularly email web page addresses to friends. Twelve people were selected to participate in this study.

\subsection{Study Environment}
Each study session lasted between thirty to forty-five minutes, with the participant sitting at a desktop computer with the Firefox browser running the application plugin. The session was a Think-Aloud study in which the participant verbally describes his/her thoughts throughout the duration of the study. A video camera captured the audio/video and was focused on the monitor screen. Before the session began, we briefly demonstrated the features of the application: how to (1) select snippets, (2) write a snippet topic and point, (3) relate points, (4) show/hide the margin, and (5) browse recent activity.

\subsection{Study Tasks}
The study consisted of two tasks to collect snippets, each lasting ten to fifteen minutes. During both tasks, we asked participants to browse the web as they normally would. In the first task, the participant browses the web about a topic or issue of their choice from the domain of politics. The collection of snippets should help the participant either argue or form an opinion/perspective about the topic, and should be thought of being used to help him/her explain or discuss the topic with a friend.  We constrained the first task to politics to increase the likelihood that the study participants would encounter similar issues and news stories.

>>>>

\todo{This interface is actually closer to TheBrain than the text suggests}

@@

Users see a claim browser in three different places:
\begin{itemize}
\item {\bf The Main Organizer} shows two claim browsers, and allows users to use drag and drop to make new connections between claims in the two organizers. (Figure~\ref{fig:claimbrowser})
\item {\bf The Popup Browser} shows one claim browser in a reduced-size window and is used to quickly investigate a claim found on a web page. (Figure~\ref{claimview})
\item {\bf The Claim Selection Window} shows one claim browser, together with the text of a new snippet, and is used to identify the claim that a snippet is making. (Figure~\ref{snipsavefull}) 
\end{itemize}

@@

Much of the value of Think Link comes from the connections between claims. It is thus important that it be easy to establish new connections between claims and topics.

Think Link uses the familiar drag and drop interface for establishing new connections. To establish a connection between two claims, one need simply drag one claim onto the other. In the full interface, one can open two browsers and drag points from one browser onto points on the other.

In our initial study, we found that many users did not realize that they could use drag and drop to create connections to existing claims. We rectify this, we added a notice at the top of the main organizer window (Figure~\ref{fig:claimbrowser}) telling users that they can use drag and drop.

We found that creating new connections between existing claims was one of the things that users found most difficult.

\todo{say more here}

@@

We performed two user studies to guide and evaluate the development of Think Link. The aim of the first study was to talk to users about the way in which they gather knowledge on the web and see how they might try to use an initial prototype of Think Link. After the first study, we revised out implementation, guided by our observations from the first study. The aim of the second study was to validate that our new design was indeed useful and to look for areas for future improvement.

\subsection{Protocol for the First Study}

For the first study, we recruited 13 paid participants. Five were female, eight were male. Their ages ranged from high school age to retired.

Our user study participants were selected from a pool of respondents to a Craigslist posting in which we asked for people who use the internet as one of their primary sources of information, regularly gather and share this information, and are interested in a new application to facilitate that process. We chose participants based on their responses to the following questions:
\begin{enumerate}
	\item What topics or types of information do you usually look for on the internet?
	\item How do usually go about finding information? (e.g. google, digg, friends, etc)
	\item How do you organize the information you find? (e.g. text file, paper, wiki, etc)
	\item How do you share information with others? (e.g. blog posts, comments, email, facebook, etc)
\end{enumerate}
We preferred individuals who search the internet for research and reading news rather than online shopping, as well as those interested in social and collaborative web activities like social networking web sites.  We were also interested in those who seemed to express a need for our application: people who copy-and-paste text from web pages into word processing documents, or who regularly email web page addresses to friends.

Each study session lasted between thirty to forty-five minutes, with the participant sitting at a desktop computer with the Firefox browser running the application plugin. The session was a Think-Aloud study in which the participant verbally describes his/her thoughts throughout the duration of the study. A video camera captured the audio/video and was focused on the monitor screen. Before the session began, we briefly demonstrated the features of the application: how to (1) select snippets, (2) write a snippet topic and point, (3) relate points, (4) show/hide the margin, and (5) browse recent activity.

The study consisted of two tasks to collect snippets, each lasting ten to fifteen minutes. During both tasks, we asked participants to browse the web as they normally would. In the first task, the participant browses the web about a topic or issue of their choice from the domain of politics. The collection of snippets should help the participant either argue or form an opinion/perspective about the topic, and should be thought of being used to help him/her explain or discuss the topic with a friend.  We constrained the first task to politics to increase the likelihood that the study participants would encounter similar issues and news stories.

\subsection{Protocol for the Second Study}

@@

\cite{scenthighlights}\cite{scenttrails}

@@

\cite{personalweb}

@@

Google Notebook
Trailfire
Zotero~\cite{zotero} is a citation mangament tool. Find and organise sources, while recording author, date etc by understanding pages. Can add notes to sources.
Scrapbook~\cite{scrapbook}

@@
